### 2016-03-16 thesis/conclusions.tex
abstract

\citet{kormendy2011} and \citet{kormendyho2013} argued that black holes correlate only 
with the remnants of major mergers, i.e.~classical bulges and elliptical galaxies, 
and that

>>>>

\citet{kormendy2011} and \citet{kormendyho2013} argued that black holes correlate only 
with the remnants of major mergers, i.e.~classical bulges and elliptical galaxies, 
and that the growth of the most massive black holes happened by means of a co-evolution with their host galaxies 
via a series of mergers and AGN feedback. 
The universality of this picture is contradicted by galaxies like Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115. 
These galaxies have classical bulges, 
they host some of the most massive black holes known ($10^9 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 10^{10}$), 
but are not the product of major mergers as the majority of today's massive elliptical galaxies. 
In effect, these galaxies have conserved their $10 \rm~Gyr$ old compact massive spheroids 
because they had little or no evolution since $z \approx 2$; 
note that $z \approx 3$ is the epoch that corresponds to the highest cosmic merger rate 
for galaxies more massive than $10^{10} \rm~M_\odot$ (e.g.~\citealt{conselice2008}).
